Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-09-19 SubGenome Analysis.Rmd
Large knit speed improvement by storing cleaned data objects in file

```{r importSynMapData, include=FALSE}
source("~/git/SubGenomes/R/loadData.R")
source("~/git/SubGenomes/R/cleanData.R")
source("~/git/SubGenomes/R/functions.R")
source("~/git/SubGenomes/R/do.R")

@@

```{r subgenome_expression_frequency, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4.5, fig.height=4}
## Plot frequency of isoform counts for each gene
data <- expressedGenes %>% inner_join(subgenome, by=c("geneID"="gene2")) %>% select(geneID, FPKM_mean, subgenome) %>% filter(subgenome=="sub1" | subgenome=="sub2")
ggplot(data, aes(FPKM_mean,color=subgenome)) + 
  geom_density() + 
  scale_x_log10() +
  labs(y = "Density (FPKM)", 
       x = "log10(FPKM)", 
       title = "Comparison of FPKM Expression between\nGenes in Subgenome 1 and Subgenome 2"
  )

>>>>

```{r importSynMapData, include=FALSE}
load("~/git/SubGenomes/Data/SavedObjects/loadedData.RData")

# source("~/git/SubGenomes/R/loadData.R")
# source("~/git/SubGenomes/R/cleanData.R")
source("~/git/SubGenomes/R/functions.R")
source("~/git/SubGenomes/R/do.R")

@@

```{r subgenome_expression_frequency, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4.5, fig.height=4}
# Paired t-test suggests that there is no difference in means between FPKM in sub1 vs. sub2:
# t.test(x=expressedPairs$FPKM_mean1, y=expressedPairs$FPKM_mean2, paired = TRUE)

## Plot frequency of isoform counts for each gene
data <- expressedGenes %>% inner_join(subgenome, by=c("geneID"="gene2")) %>% select(geneID, FPKM_mean, subgenome) %>% filter(subgenome=="sub1" | subgenome=="sub2")
ggplot(data, aes(FPKM_mean,color=subgenome)) +
  geom_density() +
  scale_x_log10() +
  labs(y = "Density (FPKM)",
       x = "log10(FPKM)",
       title = "Comparison of FPKM Expression between\nGenes in Subgenome 1 and Subgenome 2"
  )
